\documentclass[sigconf]{acmart}

\usepackage{todonotes}
\usepackage{outlines}
\usepackage{amssymb}
\usepackage{listings}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
% \acmDOI{}

% ISBN
% \acmISBN{}

%Conference
\acmConference[GECCO '17]{the Genetic and Evolutionary Computation Conference 2017}{July 15--19, 2017}{Berlin, Germany}
\acmYear{2017}
\copyrightyear{2017}

% \acmPrice{15.00}


\begin{document}
\title{Comparison of Inductive Program Synthesis Techniques applied to General Program Synthesis Problems}

\author{Edward Pantridge}
\affiliation{
	\institution{MassMutual Financial Group}
	\city{Amherst}
	\state{Massachusetts}
	\country{USA}
}
\email{epantridge@massmutal.com}

\author{Thomas Helmuth}
\affiliation{%
  \institution{Washington and Lee University}
  \city{Lexington} 
  \state{Virginia} 
}
\email{helmutht@wlu.edu}

\author{Nicholas Freitag McPhee}
\orcid{0000-0002-6495-2612}
\affiliation{%
  \institution{University of Minnesota, Morris}
  % \streetaddress{600 E. 4th Street}
  \city{Morris} 
  \state{Minnesota} 
  \postcode{56267}
}
\email{mcphee@morris.umn.edu}

\author{Lee Spector}
\affiliation{%
	\institution{Hampshire College}
	\city{Amherst}
	\state{Massachusetts}
	\country{USA}
}
\email{lspector@hampshire.edu}


\begin{abstract}
A variety of inductive program synthesis techniques have recently been developed, emerging from different areas of computer science. However, these techniques have not been adequately compared on general program synthesis problems. In this paper we compare several methods on problems requiring solution programs to handle various data types, control structures, and numbers of outputs. The problem set also spans levels of abstraction; some would ordinarily be approached using machine code or assembly language, while others would ordinarily be approached using high-level languages. The presented comparisons are focused on the possibility of success; that is, on whether the system can produce a program that passes all tests, for all training and unseen testing inputs. The compared systems are Flash Fill, Magic Haskeller, TerpreT, and two forms of genetic programming. The two genetic programming methods chosen were PushGP and Grammar Guided Genetic Programming. The results suggest that PushGP and, to an extent, TerpreT and Grammar Guided Genetic Programming are more capable of finding solutions than the others, albeit at a higher computational cost.
\todo[inline]{Keywords}
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011074.10011092.10011782.10011813</concept_id>
<concept_desc>Software and its engineering~Genetic programming</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003809.10003716.10011136.10011797.10011799</concept_id>
<concept_desc>Theory of computation~Evolutionary algorithms</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Genetic programming}
\ccsdesc[300]{Theory of computation~Evolutionary algorithms}

\keywords{ACM proceedings, \LaTeX, text tagging}


\maketitle

\input{softsynth-body}

\section{Acknowledgements}

This material is based upon work supported by the National Science Foundation under Grants No. 1617087, 1129139 and 1331283. Any opinions, findings, and conclusions or recommendations expressed in this publication are those of the authors and do not necessarily reflect the views of the National Science Foundation.

\bibliography{ss} 
\bibliographystyle{ACM-Reference-Format}

\end{document}

